Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-18 paper/Paper.tex
funding -> fueling

\section{Token Price} \label{TokenPrice}
DAO Token Creation rate decreases over time. This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full funding of the DAO. 
The DAO described in this paper has the following Creation schedule:
\begin{equation}
 P(t) = \begin{cases}
1 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
1 + 0.05 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
1.5 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenCreation} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in its base unit) each person Creates is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel a DAO, denoted in wei.
This results in a constant Creation rate in the beginning, until $2$ weeks before the end of the DAO Creation Phase. At this time the amount of ether required to Create DAO tokens increases daily by $0.05 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant Creation rate of $1.5 \: \Xi_c$ per base unit of DAO token.

@@

The map \verb|weiGiven| stores the amount of wei given by each contributor during the Creation Phase and is only used to refund the contributors if the Creation Phase does not reach its funding goal.

@@

\subsubsection*{refund}
This function can be called by any contributor to receive their wei back if the Creation Phase failed to meet its funding goal.

>>>>

\section{Token Price} \label{TokenPrice}
DAO Token Creation rate decreases over time. This reflects an assumption that early acts of DAO Creation have greater risk, as they may have less information about the potential success of the DAO and do not know whether what contribution will lead to full fueling of the DAO.
The DAO described in this paper has the following Creation schedule:
\begin{equation}
 P(t) = \begin{cases}
1 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
1 + 0.05 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
1.5 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the fueling period (see \ref{app:TokenCreation} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in its base unit) each person Creates is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether sent to fuel a DAO, denoted in wei.
This results in a constant Creation rate in the beginning, until $2$ weeks before the end of the DAO Creation Phase. At this time the amount of ether required to Create DAO tokens increases daily by $0.05 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant Creation rate of $1.5 \: \Xi_c$ per base unit of DAO token.

@@

The map \verb|weiGiven| stores the amount of wei given by each contributor during the Creation Phase and is only used to refund the contributors if the Creation Phase does not reach its fueling goal.

@@

\subsubsection*{refund}
This function can be called by any contributor to receive their wei back if the Creation Phase failed to meet its fueling goal.
